Bulk Semantic Annotation with an Partially Known Knowledge Base

### 2024-11-13 doc/cicm25-sysdesc/sysdesc.tex
more

The command-line interface is simple and responsive and gives all the necessary
information in a single glance if underlying shell area exceeds ca. $80\times 35$
characters. It is very much geared towards annotating existing documents with respect to a
relatively complete -- pre-existing -- domain model. Otherwise we have to skip too many
terms that should ultimately be annotated and annotation efficiency suffers. This is
currently the case for all non-English languages in the \sTeX commons. Coverage in German
is only about half of that of English and we can already see the practical effects. We
have also experimented with a Slovene introductory math book, and it seems clear that
apart from having to introduce a Slovene stemmer\ednote{MK@FS: there is one for python at
  \url{https://repo.ijs.si/pboskoski/slo_stemmer}}, we would need to manually annotate all
definienda in the book before we can harvest the symbol/verbalization pairs which are a
prerequisite for annotation.

>>>>

The command-line interface is simple and responsive and gives all the necessary
information in a single glance if underlying shell area exceeds ca. $80\times 35$
characters. It is very much geared towards annotating existing documents with respect to a
relatively complete -- pre-existing -- domain model, and it seems unlikely that a more
sophisticated UI would add value for this use-case.

For less complete domain models we have to skip too many terms that should ultimately be
annotated and annotation efficiency suffers. This is currently the case for all
non-English languages in the \sTeX corpus we work with. Coverage in German is only about
half of that of English and we can already see the practical effects. We have also
experimented with a Slovene introductory math book, and it seems clear that apart from
having to introduce a Slovene stemmer\ednote{MK@FS: there is one for python at
  \url{https://repo.ijs.si/pboskoski/slo_stemmer}}, we would need to manually annotate all
definienda in the book before we can harvest the symbol/verbalization pairs which are a
prerequisite for annotation.
